---
title: "p8105_hw1_zx2373"
author: "Ziyan Xu"
date: "2022-09-22"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

```{r echo = FALSE, message=FALSE}

library(ggplot2)
library(tidyverse)
library(palmerpenguins)

```

#Problem 1

###Description of data

```{r messege = FALSE}

data("penguins", package = "palmerpenguins")

skimr::skim(penguins)
  
nrow = nrow(penguins)
ncol = ncol(penguins)

penguins_colnames = colnames(penguins)

b = pull(penguins, var = flipper_length_mm)
mean_flipper = mean(b,na.rm = TRUE)

```

**There are `r n_row` rows and `r n_col` columns in the dataset. **
**It includes `r penguins_colomns` in total 8 variables. The mean of flipper length is `r mean_flipper`. **
**The other information which might be important to better understand this dataset is in the summary below.**

```{r}

summary(penguins)

```

###Scatterplot

```{r warning=FALSE}

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + geom_point(aes(color = species))
ggsave("Scatterplot.pdf",height = 4,width = 4)

```


#Problem 2

###Create a data frame
```{r messege=TRUE}

hw1_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = rep(c("a", "b", "c", "d", "e"), length.out = 10),
  vec_factor = factor(rep(c("high","middle","low"), length.out = 10))
  )

```

###Mean of variable
```{r warning=FALSE, message=FALSE}

mean(pull(hw1_df,vec_numeric))
mean(pull(hw1_df,vec_logical))
mean(pull(hw1_df,vec_char))
mean(pull(hw1_df,vec_factor))

```

**The mean of each variable in my dataframe are `r mean_change`, `r mean_logic`, `r mean_character`,`r mean_factor`. The means of character and factor vector are invalid**

###Convert logical, character and factor vectors into numbers

```{r convert, results = 'hide'}
x = as.numeric(pull(hw1_df, vec_logical))
y = as.numeric(pull(hw1_df, vec_char))
z = as.numeric(pull(hw1_df, vec_factor))
```


###Take the mean again
```{r mean_convert, echo = FALSE}
mean(pull(hm1_df, vec_numeric))
mean(x)
mean(y)
mean(z)
```

**After converting, the logical vector remains the same, which is "True = 1*" and "False = 0".** **The factor vector generates the numerical mean. But the character variable cannot be converted into numbers and are left as NA.**

