---
title: "p8105_hw1_zx2373"
author: "Ziyan Xu"
date: "2022-09-22"
output: github_document
---


```{r echo = FALSE, message=FALSE}

library(ggplot2)
library(tidyverse)

```

#Problem 1

###Description of data

```{r messege = FALSE}

data("penguins", package = "palmerpenguins")

```

* This is a tibble data frame about penguins with names of variables:  `r names(penguins)`.
* The bill length has a range of `r range(pull(penguins, bill_length_mm), na.rm = TRUE)` and a mean of `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)` mm.
* The bill depth has a range of `r range(pull(penguins, bill_depth_mm), na.rm = TRUE)` and a mean of `r mean(pull(penguins, bill_depth_mm), na.rm = TRUE)` mm.
* The flipper length has a range of `r range(pull(penguins, flipper_length_mm), na.rm = TRUE)`.
* The body mass has a range of `r range(pull(penguins, body_mass_g), na.rm = TRUE)` and a mean of `r mean(pull(penguins, body_mass_g), na.rm = TRUE)` g.
* There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in the dataset.
* The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm after removing all missing data in the flipper length column.


```{r}

summary(penguins)

```

###Scatterplot

```{r warning=FALSE}

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + geom_point(aes(color = species))
ggsave("Scatterplot.pdf",height = 4,width = 4)

```


#Problem 2

###Create a data frame
```{r messege=TRUE}

hw1_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = rep(c("a", "b", "c", "d", "e"), length.out = 10),
  vec_factor = factor(rep(c("high","middle","low"), length.out = 10))
  )

```

###Mean of variable
```{r warning=FALSE, message=FALSE}

mean(pull(hw1_df,vec_numeric))
mean(pull(hw1_df,vec_logical))
mean(pull(hw1_df,vec_char))
mean(pull(hw1_df,vec_factor))

```

* When I try to take the means of character vector and factor vector, it returns NAs because argument is not numeric or logical.


###Convert logical, character and factor vectors into numbers

```{r convert, results = 'hide'}
x = as.numeric(pull(hw1_df, vec_logical))
y = as.numeric(pull(hw1_df, vec_char))
z = as.numeric(pull(hw1_df, vec_factor))
```

**After converting, the logical vector remains the same, which is "True = 1*" and "False = 0".** **The factor vector generates the numerical mean. But the character variable cannot be converted into numbers and are left as NA.**

